The \dealii Library, Version 9.5

### 2023-07-19 9.5/paper.tex
Mention that step-64 can be used on the CPU

In the current release, \texttt{LinearAlgebra::distributed::Vector} and the 
\texttt{CUDAWrappers::Matrix\allowbreak{}Free} framework are using \kokkos. This allows them 
to work on all the architectures supported by \kokkos. The \kokkos backend used 
by \dealii is \texttt{Kokkos::DefaultExecutionSpace} which corresponds to the 
highest available backend in the hierarchy device, host-parallel, and host-serial 
at the time Kokkos was configured.

>>>>

In the current release, \texttt{LinearAlgebra::distributed::Vector} and the 
\texttt{CUDAWrappers::Matrix\allowbreak{}Free} framework are using \kokkos. This allows them 
to work on all the architectures supported by \kokkos. In particular, the step-64 example
can now also be run on the CPU and doesn't require a GPU anymore. \\
The \kokkos backend used by \dealii is \texttt{Kokkos::DefaultExecutionSpace} which corresponds
to the highest available backend in the hierarchy device, host-parallel, and host-serial 
at the time Kokkos was configured.
